---
title: "Prepare training data"
author: "Kelly Hondula"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(dplyr)
library(fasterize)
data_dir <- "/nfs/khondula-data/planetmethane"
```

# Create AOI

This creates AOI and AOI_union polygons

Download watershed boundary for 

Tuckahoe Creek
0206000501

Watts Creek-Choptank
0206000502

```{r}
download.file("https://prd-tnm.s3.amazonaws.com/StagedProducts/Hydrography/NHD/HU8/HighResolution/Shape/NHD_H_02060005_HU8_Shape.zip", "/nfs/khondula-data/planetmethane/polygons/wbd/HUC8_02060005.zip")
unzip("/nfs/khondula-data/planetmethane/polygons/wbd/HUC8_02060005.zip", 
      exdir = "/nfs/khondula-data/planetmethane/polygons/wbd")
```

# HUC 8s 

Read in USGS defined HUC 8 boundaries for Tuckahoe and Greensboro, merge into one polygon. 

```{r}
wbd <- st_read("/nfs/khondula-data/planetmethane/polygons/wbd/Shape/WBDHU10.shp") %>% 
  dplyr::filter(Name %in% c("Tuckahoe Creek", "Watts Creek-Choptank River"))
ucrw <- wbd %>% st_union()
plot(ucrw)
# st_write(ucrw, "data/UCRW.shp")
```

# HUC 12s 

Read in USGS defined HUC 12 boundaries 

```{r}
huc12 <- st_read("/nfs/khondula-data/planetmethane/polygons/wbd/Shape/WBDHU12.shp")
tuckahoe <- huc12 %>% 
  filter(HUC12 %in% grep("0206000501", huc12$HUC12, value = TRUE))
plot(tuckahoe$geometry)
watts <- huc12 %>% 
  filter(HUC12 %in% grep("0206000502", huc12$HUC12, value = TRUE))
plot(watts$geometry)
plot(tuckahoe$geometry, add = TRUE)
ucrwHUC12 <- rbind(tuckahoe, watts)
plot(ucrwHUC12$geometry)
```

```{r}
ucrwHUC12 %>%
  leaflet() %>%
  # addTiles() %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
  addPolygons(label = ~Name)
```

Subset to the top 4 headwater catchments and join them as one polygon

```{r}
AOI <- ucrwHUC12 %>% dplyr::filter(Name %in% c("Cow Marsh Creek", "Upper Mason Branch", "Tappahanna Ditch-Choptank River", "Gravelly Branch-Choptank River"))


AOI <- AOI %>% st_union(by_feature = FALSE)
plot(AOI_union)
plot(AOI$geometry)
st_write(AOI, "/nfs/khondula-data/planetmethane/polygons/AOI.shp")
st_write(AOI_union, "/nfs/khondula-data/planetmethane/polygons/AOI_union.shp")
```

```{r}
AOI %>% 
  leaflet() %>%
  # addTiles() %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
  addPolygons(label = ~Name)
```

```{r}
rm(huc12, tuckahoe, ucrw, ucrwHUC12, watts, wbd)
```

```{r}
AOI <- st_read("/nfs/khondula-data/planetmethane/polygons/AOI_union.shp")
```

# MVdeps 

Use dataset from M Vanderhoof (link)[https://www.sciencebase.gov/catalog/item/59370e80e4b0f6c2d0d899d5]

Depression IDs generated here based on entire dataset

```{r}
library(sf)
library(readr)
library(leaflet)
library(dplyr)
library(raster)
library(ggplot2)
library(stringr)
```

There are 3 files

* depressions
* Landsat 2015
* TotalStreamNetwork

```{r}
mv_dir <- "/nfs/khondula-data/Delmarva/data/vanderhoofUCRW"
# landsat <- sf::st_read(mv_dir, "Landsat_2015_UCRW") %>% st_as_sf()
mvdepressions <- sf::st_read(mv_dir, "depressions_UCRW") %>% 
  st_as_sf() 
mvdepressions <- mvdepressions %>% 
  mutate(dep_id = str_pad(1:nrow(mvdepressions), width = 5, pad = "0"))
st_write(mvdepressions, "/nfs/khondula-data/planetmethane/polygons/mvdepressions.shp")
```

```{r}
mvdepressions <- sf::st_read("/nfs/khondula-data/planetmethane/polygons/mvdepressions.shp")
head(mvdepressions)
mvdepressions_df <- mvdepressions %>% st_drop_geometry() %>%
  dplyr::mutate(area_m2 = ha*10000)

# RSQLite::dbWriteTable(planetch4_db, "mvdepressions", mvdepressions)
```

```{r}
# landsat %>% 
#   st_transform(4326) %>%
#   leaflet() %>%
#   addProviderTiles(providers$Esri.WorldImagery) %>%
#   # addTiles() %>%
#   addPolygons()
```

Leaflet map of all depressions

```{r, eval=FALSE}
mvdepressions %>% 
  st_transform(4326) %>%
  leaflet() %>%
  setView(lng = -75.825057, lat = 39.061090, zoom = 14) %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
  # addTiles() %>%
  addPolygons()
```

Leaflet map of all depressions along with WBD 

```{r, eval=FALSE}
wbd <- "https://hydro.nationalmap.gov/arcgis/services/wbd/MapServer/WMSServer"

mvdepressions %>% 
  st_transform(4326) %>%
  leaflet() %>%
  setView(lng = -75.825057, lat = 39.061090, zoom = 14) %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
  # addTiles() %>%
  addPolygons(group = "depressions") %>%
  addWMSTiles(wbd, layers = "7",
              options = WMSTileOptions(format = "image/png", transparent = TRUE),
              group = "WBD transparent") %>%
  addLayersControl(overlayGroups = c("depressions", "WBD transparent"))
```

## Size distribution of depressions

```{r}
mvdepressions %>%
  ggplot(aes(x = ha)) +
  geom_histogram() +
  scale_x_log10()
```

```{r}
mvdepressions %>%
  ggplot(aes(x = ha)) +
  stat_ecdf() +
  scale_x_log10() +
  theme_bw() + 
  ylab("Proportion") +
  xlab("Size (ha)")
```

Clip everything below some size threshold for faster plotting

```{r, eval = FALSE}
wbd <- "https://hydro.nationalmap.gov/arcgis/services/wbd/MapServer/WMSServer"

mvdepressions %>% 
  dplyr::filter(ha > 0.5) %>%
  st_transform(4326) %>%
  leaflet() %>%
  setView(lng = -75.825057, lat = 39.061090, zoom = 14) %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
  # addTiles() %>%
  addPolygons(group = "depressions", popup = ~as.character(dep_id)) %>%
  # addPolygons(data = st_transform(ucrw, 4326)) %>%
  # addWMSTiles(wbd, layers = "7",
  #             options = WMSTileOptions(format = "image/png", transparent = TRUE),
  #             group = "WBD transparent") %>%
  addLayersControl(overlayGroups = c("depressions"))
```


# Crop depressions to AOI


```{r}
planet_crs <- "+proj=utm +zone=18 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"
```

```{r}
mvdeps_cropAOI <- mvdepressions %>% 
  st_transform(planet_crs) %>% 
  st_crop(st_transform(AOI_union, planet_crs))
```

Buffer to 20m 

```{r}
mvdeps_cropAOI_buffer20m <- mvdeps_cropAOI %>% st_transform(5070) %>% 
  st_buffer(20) %>% st_transform(planet_crs)
st_write(mvdeps_cropAOI_buffer20m,
         "/nfs/khondula-data/planetmethane/polygons/mvdeps_cropAOI_buffer20m.shp")
```

# Subset depressions

Use NWI dataset to identify overlap with farm ponds and forested wetlands.


Read in NWI and crop to AOI extent

```{r}
# download.file(url = "http://www.fws.gov/wetlands/downloads/Watershed/HU8_02060005_watershed.zip", "/nfs/khondula-data/planetmethane/nwi/HU8_02060005_watershed.zip")
# unzip("/nfs/khondula-data/planetmethane/nwi/HU8_02060005_watershed.zip",
#       exdir = "/nfs/khondula-data/planetmethane/nwi/")
nwi <- sf::st_read("/nfs/khondula-data/planetmethane/nwi/HU8_02060005_Watershed",
layer = "HU8_02060005_Wetlands")
nwi_prj <- nwi %>% st_transform(crs = planet_crs)

nwi_cropAOI <- nwi_prj %>% st_crop(AOI_union)
# plot(nwi_cropAOI$geometry)

# choptank_ws <- sf::st_read("/nfs/khondula-data/planetmethane/nwi/HU8_02060005_Watershed",
# layer = "HU8_02060005_Watershed")
# choptank_ws_prj <- choptank_ws %>% 
#   st_transform(crs = planet_crs)

```

Take out farm ponds

```{r}
farmed_nwi <- dplyr::filter(nwi_cropAOI, ATTRIBUTE == "Pf")

mat <- mvdeps_cropAOI %>% st_intersects(farmed_nwi, sparse = FALSE)
depressions_pF <- which(apply(mat, 1, any))

mvdeps_cropAOI_subset <- mvdeps_cropAOI[-depressions_pF,]
```

Map

```{r}
mvdeps_cropAOI_subset %>%
  st_transform(4326) %>%
  leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
  addPolygons(color = "orange", fillOpacity = 0, label = ~as.character(dep_id)) %>%
  addPolygons(data = st_transform(AOI_union, 4326), fillOpacity = 0, color = "black")
 
```

```{r}
nwi_cropAOI_4326 <- st_transform(nwi_cropAOI, 4326)
mvdeps_cropAOI_subset_4326 <- st_transform(mvdeps_cropAOI_subset, 4326)
```


OLD below here

# Get file list

```{r}
# pdfiles <- list.files("/nfs/khondula-data/planetmethane/data", full.names = TRUE, recursive = TRUE, pattern = ".tiff")
# files <- grep("_SR.tif", pdfiles, value = TRUE)
```

Find min and max x and y bounds for files

```{r}
# filesxmin <- min(purrr::map_dbl(files, ~raster::extent(stack(.x))@xmin))
# filesxmax <- max(purrr::map_dbl(files, ~raster::extent(stack(.x))@xmax))
# filesymin <- min(purrr::map_dbl(files, ~raster::extent(stack(.x))@ymin))
# filesymax <- max(purrr::map_dbl(files, ~raster::extent(stack(.x))@ymax))
# img01_bigextent <- files[1] %>% stack() %>%
  # raster::setExtent(ext = extent(c(filesxmin, filesxmax, filesymin, filesymax)))
```

```{r}
# depressions_prj <- mvdepressions %>% st_transform(crs = proj4string(img01_bigextent))

# depressions_prj_crop <- depressions_prj %>% st_crop(st_bbox(img01_bigextent))

# sf::write_sf(wetlands_join, "../../data/NWI_wetlands_cropped.shp") # not working to save
```


Get NWI polygons for extent of image

```{r}
# transform to equal area projection (EPSG: 5070)
# depressions_prj_crop_aea <- depressions_prj_crop %>% st_transform(crs = 5070)

# # buffer  polygons to 60m
# mdnwi_60m <- st_buffer(mdnwi_aea, 60)
# # buffer  polygons to 20m
# depressions_20m <- st_buffer(depressions_prj_crop_aea, 20)
```


Crop NWI to area of depressions

```{r}
# nwi_aea <- nwi_prj %>% st_transform(crs = 5070)
# nwi_aea$WETLAND_TY %>% unique()
# nwi_forest <- dplyr::filter(nwi_aea, WETLAND_TY %in% c("Freshwater Forested/Shrub Wetland", "Freshwater Pond", "Freshwater Emergent Wetland"))
# grep("f", unique(nwi_aea$ATTRIBUTE), value = TRUE)
```

Take out farm ponds

```{r}
# farmed_nwi_crop <- farmed_nwi %>% st_crop(st_bbox(depressions_20m))

# mat <- depressions_20m %>% st_intersects(farmed_nwi_crop, sparse = FALSE)
# depressions_pF <- which(apply(mat, 1, any))

# depressions_20m_subset <- depressions_20m[-depressions_pF,]

# test2 <- depressions_20m[depressions_pF,]
```


```{r}
# test2 %>% 
  # st_transform(4326) %>%
  # leaflet() %>%
  # setView(lng = -75.825057, lat = 39.061090, zoom = 14) %>%
  # addProviderTiles(providers$Esri.WorldImagery) %>%
  # addTiles() %>%
  # addPolygons()
```






```{r}
# depressions_20m_subset_sp <- as(depressions_20m_subset, "Spatial")
# 
# depressions_20m_subset <- depressions_20m_subset %>% 
#   st_transform(crs = proj4string(raster::stack(files[1])))
# 
# selected_deps_buffer <- selected_deps_buffer %>%
#   st_transform(crs = proj4string(raster::stack(files[1])))
# 
# extract_save_ndwi <- function(imgfile){
#   wetland_polygons <- selected_deps_buffer
#   bufferdist = 20
#   wetland_type = "selected-depressions"
#   
#   imgID <- imgfile %>% basename() %>% tools::file_path_sans_ext()
#   imgstack <- raster::stack(imgfile)
#   img_vx <- velox::velox(imgstack)
#   # calculate NDWI
#   b2 <- img_vx$as.matrix(band = 2)
#   b4 <- img_vx$as.matrix(band = 4)
#   img_ndwi <- (b2-b4)/(b2+b4)
#   img_ndwi_vx <- velox::velox(img_ndwi, 
#                               extent = raster::extent(imgstack), 
#                               res = raster::res(imgstack))
#   
#   img_extract <- img_ndwi_vx$extract(wetland_polygons, df = TRUE) %>% rename(ndwi = 2)
#   
#   extract_filename <- paste0("data/ndwi_extract_data/", gsub(" ", "-", wetland_type),
#                              "_",imgID, "_", bufferdist, "m", ".csv")
#   readr::write_csv(img_extract, extract_filename)
# }
# 
# files <- fs::dir_ls("/nfs/khondula-data/planetmethane/data/")
# # extract_save_ndwi(imgfile = files[1], 
#                   # wetland_polygons = depressions_20m_subset, 
#                   # wetland_type = "depressions", bufferdist = 20)
# 
# extract_save_ndwi(files[1])
# extract_save_ndwi(files[2])
# 
# purrr::walk(files[3:10], ~extract_save_ndwi(.x))
# purrr::walk(files[11:38], ~extract_save_ndwi(.x))
# purrr::walk(files[21:30], ~extract_save_ndwi(.x))
# purrr::walk(files[31:38], ~extract_save_ndwi(.x))

```

# Selected depressions

```{r}
# selected_deps_id <- c("10127", "10112", "10162", "10367", "10097", "10002", "09829")
```

```{r}
# selected_deps_buffer <- mvdepressions %>%
#   dplyr::filter(dep_id %in% selected_deps_id) %>%
#   st_transform(5070) %>%
#   st_buffer(20)
```

```{r}
mvdepressions <- sf::st_read("/nfs/khondula-data/planetmethane/polygons/mvdepressions.shp")
```



# training data

New approach for training data 14 May 2019

Upland training data = NLCD woody wetland, etc. area MINUS all NWI area and MVdeps
Water training data = NWI ponds and lakes X mvdeps 

```{r}
planet_crs <- "+proj=utm +zone=18 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"
AOI <- st_read("/nfs/khondula-data/planetmethane/polygons/AOI_union.shp") %>% st_transform(planet_crs)
# ww_area <- st_read(file.path(data_dir, "polygons", "ww_areas.shp")) %>% st_transform(planet_crs)
# ww_areas gets made in nlcd.R file. shp file doesnt behave after being saved... 
# ww_areas_prj <- ww_areas %>% st_as_sf() %>% st_transform(planet_crs)
nwi <- st_read(file.path(data_dir, "nwi", "HU8_02060005_Watershed", "HU8_02060005_Wetlands.shp")) %>% 
                 # dplyr::filter(WETLAND_TY %in% c("Freshwater Pond", "Lake")) %>% 
                 st_transform(planet_crs)
nwi_crop <- st_join(nwi, AOI, left = FALSE) %>% st_transform(proj4string(nlcd_aoi_mask))
nwi_crop_buff30 <- nwi_crop %>% st_transform(5070) %>% 
  st_buffer(30) %>% st_transform(proj4string(nlcd_aoi_mask)) %>% st_cast(to = "POLYGON")
```

```{r}
nwi_crop_r_template <- fasterize::raster(nwi_crop_buff30, res = res(nlcd_aoi_mask), ext = extent(nlcd_aoi_mask))
nwi_crop_r <- fasterize::fasterize(nwi_crop_buff30, raster = nwi_crop_r_template, field = "WETLAND_TY")
plot(nwi_crop_r)
plot(nwi_crop)
```

THen, mask nlcd with nwi_crop_r
```{r}
# nlcd_aoi_mask %>% plot()
ww_areas_maskNWI <- raster::mask(x = nlcd_aoi_mask, mask = nwi_crop_r, inverse = TRUE)
ww_areas_maskNWI %>% plot()
```

Do same thing with mvdeps - buffer to 30m then rasterize 

```{r}
mvdeps_crop <- st_join(mvdepressions, AOI, left = FALSE) %>% st_transform(proj4string(nlcd_aoi_mask))
mvdeps_crop_buff30 <- mvdeps_crop %>% st_transform(5070) %>% 
  st_buffer(30) %>% st_transform(proj4string(nlcd_aoi_mask)) %>% st_cast(to = "POLYGON")
mvdeps_crop_r_template <- fasterize::raster(mvdeps_crop_buff30, res = res(nlcd_aoi_mask), ext = extent(nlcd_aoi_mask))
mvdeps_crop_r <- fasterize::fasterize(mvdeps_crop_buff30, raster = mvdeps_crop_r_template, field = "dep_id")
plot(mvdeps_crop_r)
```

```{r}
ww_areas_maskNWImvdeps <- raster::mask(x = ww_areas_maskNWI, mask = mvdeps_crop_r, inverse = TRUE)
ww_areas_maskNWImvdeps %>% plot()
```

```{r}
library(leaflet)
nwi_crop %>%
  st_transform(4326) %>%
  leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery) %>%
  addRasterImage(ww_areas_maskNWImvdeps) %>%
  addPolygons(opacity = 1, fillColor = "yellow", color = "black", weight = 0.5, group = "nwi") %>%
  addLayersControl(overlayGroups = c("nwi"))
```

```{r}
ww_areas_maskNWImvdeps %>% writeRaster("/nfs/khondula-data/planetmethane/ww_areas_maskNWImvdeps.tif")
```

```{r}
# library(tabularaster)
# ww <- as_tibble(ww_areas_maskNWI)
# head(ww)
```


