---
title: "methane model"
author: "Kelly Hondula"
date: "6/1/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vroom)
```

```{r}
# lo95_ts_join_rank %>% write_csv("water_area_loess_predictions.csv")
# mov_avg_ts %>% write_csv("water_area_mov_avg_predictions.csv")
```

```{r}
mvdeps_buffered_areas <- mvdeps_buffered_areas %>%
  mutate(log_area = log(ha))
```

# Holgerson area model

Log-log relationship reported in Holgreson and Raymond 2016 area is log area (ha)

```{r}
holg <- read_csv("data/holgerson-data.csv") %>%
  mutate(log_ch4 = log(ch4), log_area = log(area))
```

```{r}
lm1 <- lm(log_ch4 ~ log_area, data = holg)
summary(lm1)
```

```{r}
mvdeps_size_cats # this has all of the different areas

mvdeps_size_cats_forCH4 <- mvdeps_size_cats %>% 
  dplyr::select(dep_id, ha, max_waterpred_m2, mean_waterpred_m2, inTI) %>%
  mutate(log_max_area_ha = log(max_waterpred_m2/10000),
         log_area_ha = log(ha),
         log_mean_area_ha = log(mean_waterpred_m2/10000)) %>%
  filter(inTI)

lm1_predicts_max_area <- predict(lm1, 
                       newdata = mutate(mvdeps_size_cats_forCH4, 
                                        log_area = log_max_area_ha),
                       interval = "confidence")
lm1_predicts_mean_area <- predict(lm1, 
                       newdata = mutate(mvdeps_size_cats_forCH4, 
                                        log_area = log_mean_area_ha),
                       interval = "confidence")
lm1_predicts_mvdeps_area <- predict(lm1, 
                       newdata = mutate(mvdeps_size_cats_forCH4, 
                                        log_area = log_area_ha),
                       interval = "confidence")

max_area_ch4_ests <- mvdeps_size_cats_forCH4 %>%
  dplyr::select(dep_id) %>%
  mutate(est_fit = exp(lm1_predicts_max_area[,1]),
         est_lwr = exp(lm1_predicts_max_area[,2]),
         est_upr = exp(lm1_predicts_max_area[,3])) %>%
  tidyr::gather(est_type, ch4_umol, est_fit:est_upr) %>%
  mutate(area_type = "max_area")

mean_area_ch4_ests <- mvdeps_size_cats_forCH4 %>%
  dplyr::select(dep_id) %>%
  mutate(est_fit = exp(lm1_predicts_mean_area[,1]),
         est_lwr = exp(lm1_predicts_mean_area[,2]),
         est_upr = exp(lm1_predicts_mean_area[,3])) %>%
  tidyr::gather(est_type, ch4_umol, est_fit:est_upr) %>%
  mutate(area_type = "mean_area")

mvdeps_area_ch4_ests <- mvdeps_size_cats_forCH4 %>%
  dplyr::select(dep_id) %>%
  mutate(est_fit = exp(lm1_predicts_mvdeps_area[,1]),
         est_lwr = exp(lm1_predicts_mvdeps_area[,2]),
         est_upr = exp(lm1_predicts_mvdeps_area[,3])) %>%
  tidyr::gather(est_type, ch4_umol, est_fit:est_upr) %>%
  mutate(area_type = "mvdeps_area")

ch4_umol_predicts <- rbind(mvdeps_area_ch4_ests, max_area_ch4_ests, mean_area_ch4_ests) 

ch4_umol_predicts_wide <- ch4_umol_predicts %>% 
  mutate(ch4_umol_type = paste(est_type, area_type, sep = "-")) %>% 
  dplyr::select(dep_id, ch4_umol, ch4_umol_type) %>%
  split(ch4_umol_predicts$dep_id) %>% 
  purrr::map(~spread(.x, ch4_umol_type, ch4_umol)) %>%
  bind_rows()

# ch4_flux_predicts <- ch4_umol_predicts %>% 
#   mutate(k600 = 0.5,
#          fluxmmolm2day = k600*ch4_umol)
```

```{r}
ch4_umol_predicts_list <- ch4_umol_predicts %>%
  mutate(ch4_umol_type = paste(est_type, area_type, sep = "-")) %>% 
  dplyr::select(dep_id, ch4_umol, ch4_umol_type) %>%
  split(ch4_umol_predicts$dep_id) 

# make each list item repeat 365 times
ch4_umol_predicts_list_ts <- ch4_umol_predicts_list %>%
  purrr::map(~bind_rows(replicate(365, .x, simplify = FALSE))) %>% 
  purrr::map(~mutate(.x, date = rep(seq.Date(as.Date("2017-10-01"), as.Date("2018-09-30"), length.out = 365), each = 9)))

# then join with table from gsod to calculate fluxes
gsod_kgas_sub <- gsod_kgas %>% dplyr::select(YEARMODA, kgas05_md, satCH4_umol)

ch4_flux_predicts_list <- ch4_umol_predicts_list_ts %>% 
  purrr::map(~left_join(.x, gsod_kgas_sub, by = c("date" = "YEARMODA"))) %>% 
  purrr::map(~mutate(.x, flux_mmolm2day = kgas05_md*(ch4_umol - satCH4_umol)))
  

ch4_flux_predicts_list[[1]] %>% View()
ch4_flux_predicts_df <- ch4_flux_predicts_list %>% 
  bind_rows() 

ch4_flux_predicts_df <- ch4_flux_predicts_df %>% 
  mutate(ch4_est_type = substr(ch4_umol_type, 1, 7),
         ch4_area_type = substr(ch4_umol_type, 9, nchar(ch4_umol_type)))
# head(ch4_flux_predicts_df)
ch4_flux_predicts_df_path <- file.path(data_dir, "results/ch4_flux_predicts.tsv")
# system.time(vroom::vroom_write(ch4_flux_predicts_df, ch4_flux_predicts_df_path)) # 29,354,760 rows
# 80 seconds!
```

# Multiply by the area of each dep_id and respective area, sum across all dep_ids and by area category

Separate ch4_est type column into separate ones for area type and fit/high/low conf interval

```{r}
ch4_flux_predicts_list <- ch4_flux_predicts_list %>%
  purrr::map(~mutate(.x, ch4_est_type = substr(ch4_umol_type, 1, 7),
                     ch4_area_type = substr(ch4_umol_type, 9, nchar(ch4_umol_type))))

```

For each table, join with m2 area on dep_id and ch4_area_type to get area estimate for that wetland
Multiply flux rate and area to get emissions

```{r}
mvdeps_size_cats_forFlux <- mvdeps_size_cats %>%
  filter(inTI) %>%
  dplyr::select(dep_id, area_cat, area_m2, max_waterpred_m2, mean_waterpred_m2) %>%
  rename(mvdeps_area = area_m2, max_area = max_waterpred_m2, mean_area = mean_waterpred_m2) %>%
  tidyr::gather(ch4_area_type, area_m2, mvdeps_area:mean_area)

ch4_fluxTotal_predicts_list <- ch4_flux_predicts_list %>% 
  purrr::map(~left_join(.x, mvdeps_size_cats_forFlux, by = c("dep_id", "ch4_area_type"))) %>%
  purrr::map(~mutate(.x, flux_mmolday = flux_mmolm2day * area_m2))
```

```{r}
ch4_fluxTotal_df <- ch4_fluxTotal_predicts_list %>% bind_rows()
  
ch4_fluxTotal_predicts_df_path <- file.path(data_dir, "results/ch4_fluxTotal_predicts.tsv")
vroom::vroom_write(ch4_fluxTotal_df, ch4_fluxTotal_predicts_df_path) # 29,354,760 rows
ch4_fluxTotal_df <- vroom::vroom(ch4_fluxTotal_predicts_df_path)
head(ch4_fluxTotal_df)
```

# Summarize flux totals

Total in each size class, by day 

```{r}
fluxTotal_sum1 <- ch4_fluxTotal_df %>% 
  group_by(date, ch4_est_type, ch4_area_type, area_cat) %>%
  summarise(sum_water_area = sum(area_m2), sum_flux = sum(flux_mmolday))
fluxTotal_sum1 %>% write_csv(file.path(data_dir, "results/fluxTotal_xSizeclass_xDay.csv"))
fluxTotal_sum1 <- read_csv(file.path(data_dir, "results/fluxTotal_xSizeclass_xDay.csv"))

```

```{r}
fluxTotal_sum1 %>%
  ggplot(aes(x = date, y = sum_flux)) +
  geom_line(aes(col = area_cat)) +
  facet_grid(vars(ch4_est_type), vars(ch4_area_type)) +
  theme_bw()
```

```{r}
fluxTotal_sum1 %>%
  filter(date == "2017-10-01") %>% # water sum is same for every day
  ggplot(aes(x = area_cat, y = sum_water_area/1e6)) + # multiply by 365 for cumulative water area
  geom_bar(aes(fill = ch4_area_type), stat = "identity", position = 'dodge', color = "black") +
  theme_bw()
```

Total cumulative for each depression

```{r}
fluxTotal_sum2 <- ch4_fluxTotal_df %>% 
  group_by(dep_id, ch4_umol_type, ch4_area_type) %>%
  summarise(sum_water_area = sum(area_m2, na.rm = TRUE),
            sum_flux = sum(flux_mmolday, na.rm = TRUE))
fluxTotal_sum2 %>% write_csv(file.path(data_dir, "results/fluxTotal_xDepression.csv"))
fluxTotal_sum2 <- read_csv(file.path(data_dir, "results/fluxTotal_xDepression.csv"))

```

Total cumulative in each size class

```{r}
fluxTotal_sum3 <- ch4_fluxTotal_df %>% group_by(area_cat, ch4_est_type, ch4_area_type) %>%
  summarise(sum_water_area = sum(area_m2), sum_flux = sum(flux_mmolday, na.rm = TRUE))
fluxTotal_sum3 %>% write_csv(file.path(data_dir, "results/fluxTotal_xSizeClass.csv"))
```

```{r}
fluxTotal_sum3 %>%
  ggplot(aes(x = area_cat, y = sum_water_area/1e6)) + 
  geom_bar(aes(fill = ch4_area_type), stat = "identity", position = 'dodge', color = "black") +
  theme_bw()
```

```{r}
fluxTotal_sum3 %>%
  ggplot(aes(x = ch4_area_type, y = sum_flux/1e6)) + 
  geom_bar(aes(fill = area_cat), stat = "identity", color = "black") +
  facet_wrap(vars(ch4_est_type)) +
  theme_bw()
```

```{r}
fluxTotal_sum3 %>%
  ggplot(aes(x = ch4_area_type, y = sum_flux/1e6)) + 
  geom_bar(aes(fill = area_cat), stat = "identity", position = 'dodge', color = "black") +
  facet_wrap(vars(ch4_est_type)) +
  theme_bw()
```


# Dynamic inundation 

```{r}
head(mov_avg_ts)
mov_avg_ts_forFlux <- mov_avg_ts %>% dplyr::select(dep_id, imgDate, water_ma) %>% 
  rename(dyn_area = water_ma) %>% tidyr::gather(ch4_area_type, area_m2, dyn_area) %>% filter(!is.na(area_m2))

# ch4_flux_predicts_list[["01278"]]
results_dir <- file.path(data_dir, "results", "ch4_flux_predicts")
if(!fs::dir_exists(results_dir)){fs::dir_create(results_dir)}

# too slow to join all at once, so separate list into separate files and join one at a time
names(ch4_flux_predicts_list) %>%
  purrr::walk(~vroom_write(ch4_flux_predicts_list[[.x]], path = file.path(results_dir, sprintf("dep_id-%s.tsv", .x))))

mov_avg_ts_forFlux %>% vroom_write(file.path(data_dir, "results/mov_avg_ts_forFlux.tsv"))
# ch4_fluxTotal_predicts_list <- ch4_flux_predicts_list %>% 
#   purrr::map(~left_join(.x, mov_avg_ts_forFlux, by = c("dep_id", "ch4_area_type", "date" = "imgDate"))) %>% # large join, too slow
#   purrr::map(~mutate(.x, flux_mmolday = flux_mmolm2day * area_m2))
```

Function to do joins on cluster
```{r}
mydep_id <- dep_ids_Notcalced[1]
mydep_id
calculate_flux_dyn_area <- function(mydep_id){
  data_dir <- "/nfs/khondula-data/planetmethane"
  mov_avg_ts_forFlux <- vroom(file.path(data_dir, "results/mov_avg_ts_forFlux.tsv"))
  ch4_flux_predicts_mydep_path <- file.path(data_dir, sprintf("results/ch4_fluxRate_predicts/dep_id-%s.tsv", mydep_id))
  ch4_fluxRate_predicts_mydep <- vroom(ch4_flux_predicts_mydep_path, col_types = c("cdcDdddcc"))

ch4_flux_predicts_mydep <- ch4_fluxRate_predicts_mydep %>%
  rename(ch4_fluxrate_area_type = ch4_area_type) %>%
  dplyr::left_join(mov_avg_ts_forFlux, by = c("dep_id", "date" = "imgDate")) %>%
  dplyr::mutate(flux_mmolday = flux_mmolm2day * area_m2)

  results_dir <- file.path(data_dir, "results", "ch4_flux_predicts")
  if(!fs::dir_exists(results_dir)){fs::dir_create(results_dir)}
  vroom_write(ch4_flux_predicts_mydep, path = file.path(results_dir, sprintf("dep_id-%s.tsv", mydep_id)))
  
}
calculate_flux_dyn_area(mydep_id = names(ch4_flux_predicts_list)[2])
```


run on cluster
```{r}
library(vroom)
library(dplyr)
library(rslurm)
library(fs)
pars <- data.frame(mydep_id = dep_ids_Notcalced,
                   stringsAsFactors = FALSE)

sjob3 <- rslurm::slurm_apply(calculate_flux_dyn_area,
                            pars, 
                            jobname = "joins3", 
                            # pkgs = c("tabularaster", "fasterize", "velox", "raster", "sf", "dplyr", "readr", "tidyr", "fs"),
                            slurm_options = list(time = "1:00:00", partition = "sesync"),
                            nodes = 20, 
                            cpus_per_node = 2,
                            submit = TRUE)

rslurm::print_job_status(sjob3)
length(list.files("/nfs/khondula-data/planetmethane/results/ch4_flux_predicts/"))
dep_ids_calced <- substr(list.files("/nfs/khondula-data/planetmethane/results/ch4_flux_predicts/"), 8, 12)
length(dep_ids_calced)
dep_ids_Notcalced <- names(ch4_flux_predicts_list)[!names(ch4_flux_predicts_list) %in% dep_ids_calced]
length(dep_ids_Notcalced)
```

```{r}
data_dir <- "/nfs/khondula-data/planetmethane"
results_dir <- file.path(data_dir, "results", "ch4_flux_predicts")
ch4_fluxTotal_files <- fs::dir_ls(results_dir)
# ch4_fluxTotal_df <- vroom::vroom(ch4_fluxTotal_files, col_types = c("cdcDdddcccdd"), altrep_opts = TRUE, progress = TRUE)
# head(ch4_fluxTotal_df)
# ch4_fluxTotal_predicts_df_path <- file.path(data_dir, "results/ch4_fluxTotal_predicts_dynamic.tsv")
# vroom::vroom_write(ch4_fluxTotal_df, ch4_fluxTotal_predicts_df_path) # 29,354,760 rows
```


# Summarize flux totals - dynamic

```{r}
data_dir <- "/nfs/khondula-data/planetmethane"
results_dir <- file.path(data_dir, "results", "ch4_flux_predicts")
ch4_fluxTotal_files <- fs::dir_ls(results_dir)
```

Total in each size class, by day 

```{r}
# fluxTotal_sum1 <- ch4_fluxTotal_df %>% group_by(date, ch4_est_type, ch4_area_type, area_cat) %>%
  # summarise(sum_water_area = sum(area_m2), sum_flux = sum(flux_mmolday))
# fluxTotal_sum1 %>% write_csv(file.path(data_dir, "results/fluxTotal_xSizeclass_xDay.csv"))
```

Total cumulative for each depression

```{r}
mydep_id <- '00002'
sum_flux_dyn_area <- function(mydep_id){
  data_dir <- "/nfs/khondula-data/planetmethane"
  results_dir <- file.path(data_dir, "results", "ch4_flux_predicts")
  mydep_ch4_flux_file <- file.path(results_dir, sprintf("dep_id-%s.tsv", mydep_id))

  ch4_flux_predicts_mydep <- vroom::vroom(mydep_ch4_flux_file)
  fluxTotal_sum3 <- ch4_flux_predicts_mydep %>% group_by(dep_id, ch4_est_type, ch4_fluxrate_area_type) %>%
    summarise(sum_flux = sum(flux_mmolday, na.rm = TRUE),
              sum_water_area = sum(area_m2, na.rm = TRUE),
                  na_count = sum(is.na(flux_mmolday))) # add a column to count NAs

  results_dir <- file.path(data_dir, "results", "ch4_fluxTotal_dynamic")
  if(!fs::dir_exists(results_dir)){fs::dir_create(results_dir)}
  vroom::vroom_write(fluxTotal_sum3, path = file.path(results_dir, sprintf("dep_id-%s.tsv", mydep_id)))
  
}

sum_flux_dyn_area(mydep_id = '00003')


# length(mydep_ids)
mydep_ids <- substr(list.files(file.path(data_dir, "results", "ch4_flux_predicts")), 8, 12)
# fluxTotal_sum2 <- ch4_fluxTotal_df %>% group_by(dep_id, ch4_umol_type, ch4_area_type) %>%
#   summarise(sum_water_area = sum(area_m2), sum_flux = sum(flux_mmolday))
# fluxTotal_sum2 %>% write_csv(file.path(data_dir, "results/fluxTotal_xDepression.csv"))
```

```{r}
library(vroom)
library(dplyr)
library(rslurm)
library(fs)
pars <- data.frame(mydep_id = mydep_ids,
                   stringsAsFactors = FALSE)

sjob3 <- rslurm::slurm_apply(sum_flux_dyn_area,
                            pars, 
                            jobname = "sums", 
                            # pkgs = c("tabularaster", "fasterize", "velox", "raster", "sf", "dplyr", "readr", "tidyr", "fs"),
                            slurm_options = list(time = "3:00:00", partition = "sesync"),
                            nodes = 20, 
                            cpus_per_node = 2,
                            submit = TRUE)

rslurm::print_job_status(sjob3)

length(list.files("/nfs/khondula-data/planetmethane/results/ch4_fluxTotal_dynamic/"))
# dep_ids_calced <- substr(list.files("/nfs/khondula-data/planetmethane/results/ch4_flux_predicts/"), 8, 12)
# length(dep_ids_calced)
# dep_ids_Notcalced <- names(ch4_flux_predicts_list)[!names(ch4_flux_predicts_list) %in% dep_ids_calced]
# length(dep_ids_Notcalced)
```

# Summarizing

```{r}
data_dir <- "/nfs/khondula-data/planetmethane"
ch4_fluxTotal_files <- fs::dir_ls(file.path(data_dir, "results", "ch4_fluxTotal_dynamic"))
mvdeps_size_cats <- readr::read_csv("mvdeps_size_cats.csv") %>% 
  filter(inTI) %>%
  dplyr::select(dep_id, area_cat, area_m2)

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[1:2000],
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary01 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[2001:4000], 
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary02 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[4001:6000],
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary03 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[6001:8936],
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary04 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df_summary <- rbind(ch4_fluxTotal_df_summary01, 
                                  ch4_fluxTotal_df_summary02,
                                  ch4_fluxTotal_df_summary03,
                                  ch4_fluxTotal_df_summary04) %>%
  group_by(ch4_est_type, ch4_fluxrate_area_type, area_cat, time_series_type) %>%
  summarise(sum_flux_all_rbind = sum(sum_flux_all),
            sum_water_area_all_rbind = sum(sum_water_area_all))


# add to flux total summary 3 table
fluxTotal_sum3 <- readr::read_csv(file.path(data_dir, "results/fluxTotal_xSizeClass.csv"))
fluxTotal_sum3 <- fluxTotal_sum3 %>% 
  mutate(time_series_type = 'static')

fluxTotal_sum_x_sizecat <- ch4_fluxTotal_df_summary %>% 
  rename(sum_water_area = sum_water_area_all_rbind,
         sum_flux = sum_flux_all_rbind,
         ch4_area_type = ch4_fluxrate_area_type) %>%
  dplyr::bind_rows(fluxTotal_sum3)
```

```{r}
library(ggplot2)
fluxTotal_sum_x_sizecat %>%
  filter(ch4_est_type == 'est_fit') %>%
  ggplot(aes(x = time_series_type, y = sum_flux/1e6)) +
  geom_bar(stat = 'identity', aes(fill = area_cat)) +
  facet_wrap(vars(ch4_area_type)) +
  # facet_grid(vars(ch4_area_type), vars(ch4_est_type)) +
  theme_bw()

fluxTotal_sum_x_sizecat %>%
  ggplot(aes(x = time_series_type, y = sum_flux/1e6)) +
  geom_bar(stat = 'identity', aes(fill = area_cat), position = 'dodge') +
  facet_grid(vars(ch4_area_type), vars(ch4_est_type)) +
  theme_bw()

fluxTotal_sum_x_sizecat %>%
  tidyr::spread(ch4_est_type, sum_flux) %>%
  ggplot(aes(x = time_series_type, y = est_fit/1e6, fill = area_cat)) +
  geom_bar(stat = 'identity', position = 'dodge') +
  geom_errorbar(aes(ymax = est_upr/1e6, ymin = est_lwr/1e6), 
                width = 0.2,
                position = position_dodge(width = 0.9)) +
  facet_wrap(vars(ch4_area_type)) +
  theme_bw()

```

water area cumulative
```{r}
fluxTotal_sum_x_sizecat %>%
  ggplot(aes(x = time_series_type, y = sum_water_area/1e6)) +
  geom_bar(stat = 'identity', aes(fill = area_cat)) +
  facet_wrap(vars(ch4_area_type)) +
  theme_bw()
```

Summarize by day across size classes

```{r}
data_dir <- "/nfs/khondula-data/planetmethane"
# list.files(file.path(data_dir, "results", ))
ch4_flux_files <- fs::dir_ls(file.path(data_dir, "results", "ch4_flux_predicts"))
mvdeps_size_cats <- readr::read_csv("mvdeps_size_cats.csv") %>% 
  filter(inTI) %>%
  dplyr::select(dep_id, area_cat)
medium_deps <- mvdeps_size_cats %>% filter(area_cat == 'medium') %>% pull(dep_id)

medium_deps_files <- purrr::map_chr(medium_deps, ~grep(.x, ch4_flux_files, value = TRUE))
medium_deps_files[1] %>% read_tsv()

medium_deps_dailies <- purrr::map_df(medium_deps_files, ~read_tsv(.x, col_types = c("cdcDdddcccdd"))) %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(daily_flux_sum = sum(flux_mmolday, na.rm = TRUE),
            daily_area_sum = sum(area_m2, na.rm = TRUE)) %>% 
  mutate(time_series_type = "dynamic")

small_deps <- mvdeps_size_cats %>% filter(area_cat == 'small') %>% pull(dep_id)
small_deps_files <- purrr::map_chr(small_deps, ~grep(.x, ch4_flux_files, value = TRUE))

small_deps_dailies <- purrr::map_df(small_deps_files, ~read_tsv(.x, col_types = c("cdcDdddcccdd"))) %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(daily_flux_sum = sum(flux_mmolday, na.rm = TRUE),
            daily_area_sum = sum(area_m2, na.rm = TRUE)) %>% 
  mutate(time_series_type = "dynamic")

smallest_deps <- mvdeps_size_cats %>% filter(area_cat == 'smallest') %>% pull(dep_id)
smallest_deps_files <- purrr::map_chr(smallest_deps, ~grep(.x, ch4_flux_files, value = TRUE))

smallest_deps_dailies <- purrr::map_df(smallest_deps_files, ~read_tsv(.x, col_types = c("cdcDdddcccdd"))) %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(daily_flux_sum = sum(flux_mmolday, na.rm = TRUE),
            daily_area_sum = sum(area_m2, na.rm = TRUE)) %>% 
  mutate(time_series_type = "dynamic")

largest_deps <- mvdeps_size_cats %>% filter(area_cat == 'largest') %>% pull(dep_id)
largest_deps_files <- purrr::map_chr(largest_deps, ~grep(.x, ch4_flux_files, value = TRUE))

largest_deps_dailies <- purrr::map_df(largest_deps_files, ~read_tsv(.x, col_types = c("cdcDdddcccdd"))) %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, area_cat) %>%
  summarise(daily_flux_sum = sum(flux_mmolday, na.rm = TRUE),
            daily_area_sum = sum(area_m2, na.rm = TRUE)) %>% 
  mutate(time_series_type = "dynamic")

daily_fluxsums <- rbind(largest_deps_dailies, medium_deps_dailies, small_deps_dailies, smallest_deps_dailies)
fluxTotal_sum1 <- readr::read_csv(file.path(data_dir, "results/fluxTotal_xSizeclass_xDay.csv")) %>%
  mutate(time_series_type = 'static') %>%
  rename(daily_flux_sum = sum_flux, daily_area_sum = sum_water_area,
         ch4_fluxrate_area_type = ch4_area_type)
daily_fluxsums_rbind <- daily_fluxsums %>% bind_rows(fluxTotal_sum1)
daily_fluxsums_rbind %>% write_tsv("/nfs/khondula-data/planetmethane/results/daily_fluxsums_rbind.tsv")
```

```{r}
daily_fluxsums_rbind <- readr::read_tsv("/nfs/khondula-data/planetmethane/results/daily_fluxsums_rbind.tsv")
```

```{r}
daily_fluxsums_rbind %>%
  filter(ch4_est_type == 'est_fit') %>%
  ggplot(aes(x = date, y = daily_flux_sum/1e6, group = area_cat)) +
  geom_line(aes(color = area_cat)) +
  geom_line(aes(color = area_cat), lwd = 0.5) +
  facet_grid(vars(ch4_fluxrate_area_type), vars(time_series_type)) +
  theme_bw()
```

```{r}
daily_fluxsums %>%
  ggplot(aes(x = date, y = daily_flux_sum, color = time_series_type)) +
  geom_line() +
  facet_grid(vars(ch4_est_type), vars(ch4_fluxrate_area_type)) +
  theme_bw()
```

```{r}
daily_fluxsums_rbind %>%
  # filter(ch4_est_type == 'est_fit') %>%
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, time_series_type) %>%
  summarise(daily_flux_sum_allsizes = sum(daily_flux_sum))
```


```{r}
daily_fluxsums_rbind %>%
  # filter(ch4_est_type == 'est_fit') %>%
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, time_series_type) %>%
  summarise(daily_flux_sum_allsizes = sum(daily_flux_sum)) %>%
  ggplot(aes(x = date, y = daily_flux_sum_allsizes/1e6)) +
  geom_line(aes(color = time_series_type)) +
  # geom_line(data = filter(daily_fluxsums_rbind, ch4_est_type == 'est_upr'),
  #           aes(color = area_cat), alpha = 0.5, lty = 1) +
  # geom_line(data = filter(daily_fluxsums_rbind, ch4_est_type == 'est_lwr'),
  #           aes(color = area_cat), alpha = 0.5, lty = 1) +
  facet_grid(vars(ch4_fluxrate_area_type), vars(ch4_est_type)) +
  theme_bw()
```

Trying geom ribbon for fit upr and lower
```{r}
fit_uprs <- daily_fluxsums_rbind %>% filter(ch4_est_type != 'est_fit') %>% 
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, time_series_type) %>%
  summarise(daily_flux_sum_allsizes = sum(daily_flux_sum)) %>%
  tidyr::spread(ch4_est_type, daily_flux_sum_allsizes)
  
daily_fluxsums_rbind %>%
  filter(ch4_est_type == 'est_fit') %>%
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, time_series_type) %>%
  summarise(daily_flux_sum_allsizes = sum(daily_flux_sum)/1e6) %>%
  ggplot(aes(x = date)) +
  geom_ribbon(data = fit_uprs, aes(ymin = est_lwr/1e6, ymax = est_upr/1e6, fill = time_series_type),
                                   alpha = 0.25) +
  geom_line(aes(y = daily_flux_sum_allsizes, color = time_series_type), lwd = 1.25) +
  facet_grid(vars(ch4_fluxrate_area_type)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")
```

Cumulative water area plot
```{r}
daily_fluxsums_rbind %>% 
    filter(ch4_est_type != 'est_fit') %>%
  dplyr::select(- daily_flux_sum) %>%
  group_by(date, time_series_type, ch4_fluxrate_area_type) %>%
  summarise(daily_area_total = sum(daily_area_sum, na.rm = TRUE)) %>%
  arrange(date) %>% 
  ungroup() %>%
  group_by(time_series_type, ch4_fluxrate_area_type) %>%
  mutate(qum_area_sum = cumsum(daily_area_total)) %>% ungroup() %>%
   ggplot(aes(x = date)) +
  geom_line(aes(y = qum_area_sum/1e6, color = time_series_type), lwd = 1.25) +
  facet_wrap(vars(ch4_fluxrate_area_type)) +
  theme_bw() +   scale_color_brewer(palette = "Dark2")

```

Try cumulative ribbon plot
```{r}
fit_uprs_qum <- daily_fluxsums_rbind %>% 
    filter(ch4_est_type != 'est_fit') %>%
  group_by(date, ch4_est_type, ch4_fluxrate_area_type, time_series_type) %>%
  summarise(daily_flux_sum = sum(daily_flux_sum, na.rm = TRUE)) %>%
  arrange(date) %>% 
  ungroup() %>%
  group_by(ch4_est_type, ch4_fluxrate_area_type, time_series_type) %>%
  mutate(qum_flux_sum = cumsum(daily_flux_sum)) %>% ungroup() %>%
  dplyr::select(-daily_flux_sum) %>%
  spread(ch4_est_type, qum_flux_sum)

daily_fluxsums_rbind %>% 
  filter(ch4_est_type == 'est_fit') %>%
  group_by(date, ch4_fluxrate_area_type, time_series_type) %>%
  summarise(daily_flux_sum = sum(daily_flux_sum, na.rm = TRUE)) %>%
  arrange(date) %>% 
  ungroup() %>%
  group_by(ch4_fluxrate_area_type, time_series_type) %>%
  mutate(qum_flux_sum = cumsum(daily_flux_sum)) %>%
  ggplot(aes(x = date)) +
  geom_ribbon(data = fit_uprs_qum, aes(ymin = est_lwr/1e6, ymax = est_upr/1e6, fill = time_series_type),
                                   alpha = 0.25) +
  geom_line(aes(y = qum_flux_sum/1e6, color = time_series_type), lwd = 1.25) +
  facet_grid(vars(ch4_fluxrate_area_type), scales = "free") +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

```

```{r}
daily_fluxsums_rbind %>% 
  filter(ch4_est_type == 'est_fit') %>%
  group_by(date, ch4_fluxrate_area_type, time_series_type) %>%
  summarise(daily_flux_sum = sum(daily_flux_sum, na.rm = TRUE)) %>%
  arrange(date) %>% 
  ungroup() %>%
  group_by(ch4_fluxrate_area_type, time_series_type) %>%
  mutate(qum_flux_sum = cumsum(daily_flux_sum)) %>%
  ggplot(aes(x = date)) +
  geom_ribbon(data = fit_uprs_qum, aes(ymin = est_lwr/1e6, ymax = est_upr/1e6, fill = ch4_fluxrate_area_type),
                                   alpha = 0.25) +
  geom_line(aes(y = qum_flux_sum/1e6, color = ch4_fluxrate_area_type), lwd = 1.25) +
  facet_wrap(vars(time_series_type), ncol = 2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

```

```{r}
fit_uprs2 <- daily_fluxsums_rbind %>% 
  filter(ch4_est_type != 'est_fit') %>% 
  # group_by(date, ch4_est_type, ch4_fluxrate_area_type, time_series_type) %>%
  # summarise(daily_flux_sum_allsizes = sum(daily_flux_sum)) %>%
  tidyr::spread(ch4_est_type, daily_flux_sum)
  
daily_fluxsums_rbind %>%
  filter(ch4_est_type == 'est_fit') %>%
  ggplot(aes(x = date, group = time_series_type)) +
  geom_ribbon(data = fit_uprs2, aes(ymin = est_lwr/1e6, ymax = est_upr/1e6,
                                    fill = time_series_type), alpha = 0.25) +
  geom_line(aes(color = time_series_type, y = daily_flux_sum/1e6)) +
  facet_grid(vars(ch4_fluxrate_area_type), vars(area_cat)) +
  theme_bw()
```

Plot mvdeps area vs mean area

```{r}
 readr::read_csv("mvdeps_size_cats.csv") %>% 
  filter(inTI) %>%
  filter(area_cat != "largest") %>%
  ggplot(aes(x = area_m2, y = mean_waterpred_m2)) +
  geom_abline(slope = 1, intercept = 0, lty = 2, col = "red") +
  geom_point(alpha = 0.25) +
  geom_abline(slope = 1, intercept = 0, lty = 2, col = "red") +
  geom_smooth(method = "lm") +
  theme_bw() +
  expand_limits(y = 0, x = 0) +
  # scale_x_log10() + scale_y_log10() +
  facet_wrap(vars(area_cat), ncol = 1, scales = "free")
```

# Percent of total flux from water bodies with different sizes

Summarize total by depression
```{r}
data_dir <- "/nfs/khondula-data/planetmethane"
ch4_fluxTotal_files <- fs::dir_ls(file.path(data_dir, "results", "ch4_fluxTotal_dynamic"))
mvdeps_size_cats <- readr::read_csv("mvdeps_size_cats.csv") %>% 
  filter(inTI) %>%
  dplyr::select(dep_id, area_cat, area_m2)

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[1:2000],
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary01 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(dep_id, ch4_est_type, ch4_fluxrate_area_type) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[2001:4000], 
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary02 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(dep_id, ch4_est_type, ch4_fluxrate_area_type) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[4001:6000],
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary03 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(dep_id, ch4_est_type, ch4_fluxrate_area_type) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df <- purrr::map_df(ch4_fluxTotal_files[6001:8936],
                                  ~readr::read_tsv(.x, col_types = "cccddc"))

ch4_fluxTotal_df_summary04 <- ch4_fluxTotal_df %>% 
  left_join(mvdeps_size_cats) %>% 
  group_by(dep_id, ch4_est_type, ch4_fluxrate_area_type) %>%
  summarise(sum_flux_all = sum(sum_flux),
            sum_water_area_all = sum(sum_water_area)) %>%
  mutate(time_series_type = 'dynamic')

ch4_fluxTotal_df_summary <- rbind(ch4_fluxTotal_df_summary01, 
                                  ch4_fluxTotal_df_summary02,
                                  ch4_fluxTotal_df_summary03,
                                  ch4_fluxTotal_df_summary04)


```

## compute ecdf values

```{r}
# fluxTotal_sum2_forjoin <- ch4_fluxTotal_df_summary %>% 
#   dplyr::select(dep_id, sum_water_area_all, sum_flux_all) %>% ungroup() %>%
#   rename(sum_static_water_area = sum_water_area_all, sum_static_flux = sum_flux_all) %>%
#   filter(ch4_umol_type == 'est_upr-mvdeps_area') %>% dplyr::select(-ch4_umol_type)

fluxTotal_sum2_forjoin_upr_mean <- fluxTotal_sum2 %>% 
  dplyr::select(dep_id, sum_water_area, sum_flux) %>% ungroup() %>%
  rename(sum_static_water_area = sum_water_area, sum_static_flux = sum_flux) %>%
  filter(ch4_umol_type == 'est_upr-mean_area') %>% dplyr::select(-ch4_umol_type)
fluxTotal_sum2_forjoin_fit <- fluxTotal_sum2 %>% 
  dplyr::select(dep_id, sum_water_area, sum_flux) %>% ungroup() %>%
  rename(sum_static_water_area = sum_water_area, sum_static_flux = sum_flux) %>%
  filter(ch4_umol_type == 'est_fit-mvdeps_area') %>% dplyr::select(-ch4_umol_type)
fluxTotal_sum2_forjoin_lwr <- fluxTotal_sum2 %>% 
  dplyr::select(dep_id, sum_water_area, sum_flux) %>% ungroup() %>%
  rename(sum_static_water_area = sum_water_area, sum_static_flux = sum_flux) %>%
  filter(ch4_umol_type == 'est_lwr-mvdeps_area') %>% dplyr::select(-ch4_umol_type)

ch4_fluxTotal_ecdf <- ch4_fluxTotal_df_summary %>%
  filter(ch4_est_type == 'est_upr', ch4_fluxrate_area_type == 'mvdeps_area') %>%
  left_join(mvdeps_size_cats) %>% 
  left_join(fluxTotal_sum2_forjoin) %>%
  arrange(area_m2) %>% ungroup() %>% 
  filter(!is.na(sum_static_flux)) %>% # not sure why there are NAs here
  mutate(flux_qum = cumsum(sum_flux_all)) %>%
  mutate(flux_qum_scale = flux_qum/max(flux_qum)) %>%
  mutate(static_area_yr = area_m2*365) %>%
  mutate(static_area_qum = cumsum(static_area_yr)) %>%
  mutate(static_area_qum_scale = static_area_qum/max(static_area_qum)) %>%
  mutate(area_qum = cumsum(sum_water_area_all)) %>%
  mutate(area_qum_scale = area_qum/max(area_qum)) %>%
  mutate(static_flux_qum = cumsum(sum_static_flux)) %>%
  mutate(static_flux_qum_scale = static_flux_qum/max(static_flux_qum, na.rm = TRUE))

filter(ch4_fluxTotal_ecdf, area_m2 < (30*30)) %>%
  summarise(flux_prop = sum(sum_flux_all)) %>% 
  pull(flux_prop)/max(ch4_fluxTotal_ecdf$flux_qum)

filter(ch4_fluxTotal_ecdf, area_m2 < (30*30)) %>%
  summarise(water_prop = sum(sum_water_area_all)) %>%
  pull(water_prop)/max(ch4_fluxTotal_ecdf$area_qum)

filter(ch4_fluxTotal_ecdf, area_m2 < (10000)) %>%
  summarise(water_prop = sum(sum_water_area_all)) %>%
  pull(water_prop)/max(ch4_fluxTotal_ecdf$area_qum)

filter(ch4_fluxTotal_ecdf, area_m2 < (30*30)) %>%
  summarise(water_prop = sum(static_area_yr)) %>% 
  pull(water_prop)/max(ch4_fluxTotal_ecdf$static_area_qum)
filter(ch4_fluxTotal_ecdf, area_m2 < (30*30)) %>%
  summarise(flux_prop = sum(sum_static_flux)) %>% 
  pull(flux_prop)/max(ch4_fluxTotal_ecdf$static_flux_qum)

# find proportion of all emissions below 30 x 30 size
f2 <- ch4_fluxTotal_ecdf %>% 
  ggplot(aes(x = area_m2/1e6)) +
  geom_line(aes(y = flux_qum_scale), color = "purple", lwd = 1) +
  geom_line(aes(y = area_qum_scale), color = "blue", lwd = 1) +
  # geom_line(aes(y = static_area_qum_scale), col = "blue", lty = 2) +
  # geom_line(aes(y = static_flux_qum_scale), col = "purple", lty = 2) +
  geom_vline(xintercept = (30*30)/1e6, lty = 2) +
  scale_x_log10() + theme_bw() +
    xlab("Water body size (km2)") +
  ylab("Proportion of cumulative")

pdf("fluxArea_ecdf_ts.pdf", width = 5, height = 4)
print(f2)
dev.off()

ch4_fluxTotal_ecdf %>% 
  ggplot(aes(x = area_m2/1e6)) +
  geom_line(aes(y = flux_qum), color = "purple", lwd = 2) +
  # geom_line(aes(y = area_qum_scale), color = "blue", lwd = 2) +
  # geom_line(aes(y = static_area_qum_scale), col = "blue", lty = 2) +
  geom_line(aes(y = static_flux_qum), col = "purple", lty = 2) +
  geom_vline(xintercept = (30*30)/1e6, lty = 2) +
  scale_x_log10() + theme_bw() +
    xlab("Water body size (km2)") +
  ylab("cumulative")

ch4_fluxTotal_ecdf %>% 
  ggplot(aes(x = area_m2/1e6)) +
  # geom_line(aes(y = flux_qum), color = "purple", lwd = 2) +
  geom_line(aes(y = area_qum), color = "blue", lwd = 2) +
  geom_line(aes(y = static_area_qum), col = "blue", lty = 2) +
  # geom_line(aes(y = static_flux_qum), col = "purple", lty = 2) +
  geom_vline(xintercept = (30*30)/1e6, lty = 2) +
  scale_x_log10() + theme_bw() +
    xlab("Water body size (km2)") +
  ylab("cumulative")
```


