---
title: "Double counting"
author: "Kelly Hondula"
date: "6/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(vroom)
library(fs)
library(dplyr)
library(raster)
library(sf)
library(purrr)
```

Water cells in multiple polygons in each image. Filter cell IDs to mvdeps and water, then group by cell ID

```{r}
rf_predicts_files <- fs::dir_ls("/nfs/khondula-data/planetmethane/results/rf_predicts_noEHW_pixels")
rf_predicts_file <- rf_predicts_files[1]
```

On one image

```{r}
# read in
rf_predicts <- rf_predicts_file %>% 
  vroom::vroom(col_types = c("iddddddddddddlllcddcc")) %>%
  dplyr::select(cellindex, water_training, mvdeps, imgID, x, y, ID_sp, ranger_predict)
# filter to water and find double counts
rf_predicts_dc <- rf_predicts %>% 
  filter(mvdeps, ranger_predict == 'water') %>% 
  group_by(cellindex, x, y) %>%
  summarise(n_polygons = n()) %>% 
  arrange(desc(n_polygons)) %>% 
  filter(n_polygons > 1)
```

Now for each cell index, need to assign it to a polygon ID_sp based on polygon that is closest to cell index xy
```{r}
my_cellindices <- rf_predicts_dc[['cellindex']]
my_cellindx <- my_cellindices[1]
# mvdeps_overlaps <- rf_predicts %>% 
#   dplyr::filter(cellindex == my_cellindx) %>%
#   pull(ID_sp)
```

```{r}
# masked_layer_files <- fs::dir_ls("data/imgs_for_analysis")
# masked_layer_files_nfs <- gsub("data", "/nfs/khondula-data/planetmethane", masked_layer_files)
# 
# img_file <- rf_predicts_file %>%
#   basename() %>% 
#   substr(11, 30) %>%
#   grep(masked_layer_files_nfs, value = TRUE)
# 
# # load in image and the overlapping polygons
# imgstack <- raster::stack(img_file)[[1]]
# mvdeps_sf <- st_read("/nfs/khondula-data/planetmethane/polygons/mvdeps_buff20_inNLCD.shp")
# mvdeps_sub <- mvdeps_sf %>%
#   dplyr::filter(dep_id %in% mvdeps_overlaps)
# mvdeps_centroids <- mvdeps_sub %>% sf::st_centroid()
# 
# centroid_xys <- raster::extract(imgstack, mvdeps_centroids, cellnumbers = TRUE, df = TRUE) %>%
#   dplyr::pull(cells) %>%
#   purrr::map(~as.data.frame(raster::xyFromCell(imgstack, cell = .x))) %>% 
#   bind_rows() %>% 
#   mutate(dep_id = mvdeps_overlaps) 
# 
# centroids_sf <- st_as_sf(centroid_xys, coords = c("x", "y"))
# mycell_sf <- raster::xyFromCell(imgstack, cell = my_cellindx) %>% st_point()
# 
# mvdep_closest <- mvdeps_overlaps[which.min(st_distance(mycell_sf, centroids_sf))]
```

Define Function to return id of closest mvdep given an image and cellindex

```{r}
find_doublcount_mvdeps <- function(rf_predicts_file, my_cellindx){
  masked_layer_files <- fs::dir_ls("/nfs/khondula-data/planetmethane/imgs_for_analysis")
  img_file <- rf_predicts_file %>%
    basename() %>% 
    substr(11, 30) %>%
    grep(masked_layer_files, value = TRUE)
  thisimgID <- img_file %>% basename() %>% tools::file_path_sans_ext()
  
  mvdeps_overlaps <- rf_predicts_file %>% 
    vroom::vroom(col_types = c("iddddddddddddlllcddcc")) %>%
    dplyr::filter(cellindex == my_cellindx) %>%
    dplyr::pull(ID_sp)
  
  # load in image and the overlapping polygons
  imgstack <- raster::stack(img_file)[[1]]
  mvdeps_sf <- st_read("/nfs/khondula-data/planetmethane/polygons/mvdeps_buff20_inNLCD.shp")
  mvdeps_centroids <- mvdeps_sf %>%
    dplyr::filter(dep_id %in% mvdeps_overlaps) %>% 
    sf::st_centroid()

  centroid_xys <- raster::extract(imgstack, mvdeps_centroids, cellnumbers = TRUE, df = TRUE) %>%
    dplyr::pull(cells) %>%
    purrr::map(~as.data.frame(raster::xyFromCell(imgstack, cell = .x))) %>% 
    dplyr::bind_rows() %>% 
    dplyr::mutate(dep_id = mvdeps_overlaps) 

  centroids_sf <- sf::st_as_sf(centroid_xys, coords = c("x", "y"))
  mycell_sf <- raster::xyFromCell(imgstack, cell = my_cellindx) %>% st_point()

  mvdep_closest <- mvdeps_overlaps[which.min(st_distance(mycell_sf, centroids_sf))]
  mvdep_dc <- mvdeps_overlaps[-which.min(st_distance(mycell_sf, centroids_sf))]
  return_df <- data.frame("cellindex" = my_cellindx, 
                          "dep_id_dc" = as.character(mvdep_dc),
                          "remove_dc" = TRUE,
                          stringsAsFactors = FALSE)
  # save results 
  data_dir <- "/nfs/khondula-data/planetmethane"
  dc_dir <- file.path(data_dir, "metadata", "double_count_cells", thisimgID)
  if(!fs::dir_exists(dc_dir)){fs::dir_create(dc_dir)}

  df_filename <- file.path(dc_dir, sprintf("%s.csv", my_cellindx))
  readr::write_csv(return_df, df_filename)
}
```

Apply function
```{r}

dc_mvdeps_rf1 <- purrr::map_df(my_cellindices[1:10],
                                     ~find_doublcount_mvdeps(rf_predicts_files[1], 
                                                         my_cellindx = .x))

```

Figure out cell numbers for given image
```{r}
# rf_predicts_files <- fs::dir_ls("/nfs/khondula-data/planetmethane/results/rf_predicts_noEHW_pixels_v2")
# rf_predicts_file <- rf_predicts_files[1]

get_my_cellindices <- function(rf_predicts_file){
  my_cellindices <- rf_predicts_file %>% 
    vroom::vroom(col_types = c("iddddddddddddlllcddcc")) %>%
    filter(mvdeps, ranger_predict == 'water') %>% 
    group_by(cellindex, x, y) %>%
    summarise(n_polygons = n()) %>% 
    filter(n_polygons > 1) %>% 
    pull(cellindex)
  return(my_cellindices)
}

# my_cellindices <- get_my_cellindices(rf_predicts_files[2])
```

```{r}
rf_predicts_files <- fs::dir_ls("/nfs/khondula-data/planetmethane/results/rf_predicts_noEHW_pixels_v2")
rf_predicts_ids <- substr(basename(rf_predicts_files), 11, 30)
dbbl_count_ids <- list.files('data/metadata/double_count_cells')
need_dbbl_count_ids <- rf_predicts_files[!rf_predicts_ids %in% dbbl_count_ids]
```

Get parameters to run on cluster
```{r}
library(dplyr)
cell_inds <- purrr::map(need_dbbl_count_ids, ~get_my_cellindices(.x))
names(cell_inds) <- need_dbbl_count_ids
head(cell_inds)
cell_inds[[1]] %>% as.data.frame() %>% rename(my_cellindx = 1) %>% head()
# for each item in list, make into a data frame with columns for rf_predicts_file and my_cellindx
pars <- purrr::map_df(cell_inds, ~as.data.frame(.x), .id = 'rf_predicts_file') %>% 
  rename(my_cellindx = 2)
head(pars)
```

Run on cluster
```{r}
library(rslurm)
# dont forget to load libraries!
# my_cellindices <- get_my_cellindices(rf_predicts_files[5])
# pars <- data.frame("rf_predicts_file" = rep(rf_predicts_files[5], length(my_cellindices)),
#                    "my_cellindx" = my_cellindices,
#                    stringsAsFactors = FALSE)

sjob12 <- rslurm::slurm_apply(find_doublcount_mvdeps, pars, 
                            jobname = "dbbl_6",
                            slurm_options = list(partition = "sesync"),
                            nodes = 12,
                            cpus_per_node = 2,
                            submit = TRUE)
rslurm::print_job_status(sjob12)
```

```{r}
length(list.files('data/metadata/double_count_cells')) # should get up to 297 (based on RF files)
```


## Update rf_predicts files

Once all the double counted cells for an image are run through the find doublecount mvdeps function, Then use the closest mvdeps data frame to update rf_predicts file, new row to filter out the polygons that are double counts


```{r}
rf_predicts_files <- fs::dir_ls("/nfs/khondula-data/planetmethane/results/rf_predicts_noEHW_pixels_v2")
rf_predicts_ids <- substr(basename(rf_predicts_files), 11, 30)
rf_predicts_id <- rf_predicts_ids[1]
```

```{r}
save_rf_updates <- function(rf_predicts_id){
  rf_predicts_files <- fs::dir_ls("/nfs/khondula-data/planetmethane/results/rf_predicts_noEHW_pixels_v2")
  dc_dirs <- fs::dir_ls("/nfs/khondula-data/planetmethane/metadata/double_count_cells/")
  
  rf_predicts_file <- rf_predicts_files[grep(rf_predicts_id, rf_predicts_files)]
  dc_dir <- dc_dirs[grep(rf_predicts_id, dc_dirs)]
  # read in rf_predicts data
  rf_predicts <- rf_predicts_file %>% 
    vroom::vroom(col_types = c("iddddddddddddlllcddcc")) %>%
    dplyr::select(cellindex, water_training, mvdeps, imgID, x, y, ID_sp, ranger_predict)
  # read in double count data
  dc_files <- fs::dir_ls(dc_dir)
  dc_mvdeps_rf1 <- purrr::map_df(dc_files, ~readr::read_csv(.x, col_types = c("icl")))
  # merge
  rf_predicts_update <- rf_predicts %>%
    dplyr::left_join(dc_mvdeps_rf1, by = c("cellindex", "ID_sp" = "dep_id_dc")) %>%
    dplyr::mutate(remove_dc = tidyr::replace_na(remove_dc, FALSE))
  # save updated data
  data_dir <- "/nfs/khondula-data/planetmethane"
  df_filename <- file.path(data_dir, "results", "rf_predicts_wdc", sprintf("%s.csv", rf_predicts_id))
  readr::write_csv(rf_predicts_update, df_filename)
}
```

Run on cluster
```{r}
library(rslurm)
# dont forget to load libraries!
rf_predicts_ids <- basename(list.files('data/metadata/double_count_cells'))
pars <- data.frame("rf_predicts_id" = rf_predicts_ids,
                   stringsAsFactors = FALSE)

sjob12 <- rslurm::slurm_apply(save_rf_updates, pars, 
                            jobname = "dcupdates",
                            slurm_options = list(partition = "sesync"),
                            nodes = 12,
                            cpus_per_node = 2,
                            submit = TRUE)
rslurm::print_job_status(sjob12)
```

FIN
